Learning Discrete-valued Bayesian Networks from Mixed Data

### 2015-11-17 BN_discretizer_paper.tex
Exp part update

\begin{figure}[ht]
    \begin{tabular}{cc}
      \input{graph_wine_exp1_distr}
    \end{tabular}
  \caption{Comparison of the raw data and discretization result on variable $A$ and $C$ according to Figure \ref{Auto_graph_2} and Table \ref{Auto_MPG_disc_table_2}}
  \label{wine_exp1_distr}
\end{figure}

@@

Figure \ref{Wine_graph_2} is the learned discrete-valued Bayesian network, which is obtained by running Algorithm \ref{alg:structure_learn} 50 times. The integer numbers next to variables are cardinality numbers of variables. By comparing Figure \ref{Wine_graph_2} with \ref{Wine_graph_1}, it shows that the the Bayesian network obtained by \ref{alg:structure_learn} has more edges than the network obtained by prediscretization and the K2 algorithm. Furthermore, the cardinalitis of discretized variables in Figure \ref{Wine_graph_2} are smaller than the result in \ref{Wine_disc_table_1}.

Figure \ref{wine_exp2_distr_5_11} shows the discretization result on variable $E$ and $K$. The discretization edge on variable $E$ is same as the edge found by the MDL principle and the proposed method in Figure \ref{wine_exp1_distr}. This indicates that some discretization edges are robust against the network structure.

\begin{figure}[ht]
    \begin{tabular}{cc}
    \centering
    \scalebox{0.7}{
      \input{graph_wine_2}}
    \end{tabular}
  \caption{The learned discrete-valued Bayesian network from the Wine dataset}
  \label{Wine_graph_2}
\end{figure}

\begin{figure}[ht]
    \begin{tabular}{cc}
      \input{graph_wine_exp2_distr_5_11}
    \end{tabular}
  \caption{Comparison of the raw data and discretization result on variable $E$ and $K$ according to Figure \ref{Auto_graph_2}}
  \label{Wine_graph_2}
\end{figure}

>>>>

Figure \ref{fig:wine_exp1_distr} compares the discretization results by the proposed method and the MDL method. It shows the discretization edges on variable $E$ and $K$, and the probability of resulting discretized area. The proposed method has more discretization edges than the MDL method. Furthermore, the discretization edges on $E$ and $K$ obtained by the MDL method are either included in or close to the edges by obtained proposed method. This indicates that the proposed method can include the discretization result obtained by the MDL method and meanwhile, capture other discretization edges without significantly increase cardinality numbers of variables.

\begin{figure}[ht]
    \begin{tabular}{cc}
      \input{graph_wine_exp1_distr}
    \end{tabular}
  \caption{Comparison of the discretization results on variable $A$ and $C$ obtained by the proposed method and the MDL method}
  \label{fig:wine_exp1_distr}
\end{figure}

@@

Figure \ref{fig:wine_graph_2} is the learned discrete-valued Bayesian network from the Wine dataset, and it is obtained by running Algorithm \ref{alg:structure_learn} 50 times. The integer numbers next to variables are cardinality numbers of variables. By comparing Figure \ref{fig:wine_graph_2} with \ref{fig:wine_graph_1}, it shows that the the Bayesian network obtained by \ref{alg:structure_learn} has more edges than the network obtained by prediscretization and the K2 algorithm. Furthermore, the cardinalitis of discretized variables in Figure \ref{fig:wine_graph_2} are smaller than the result in \ref{fig:wine_disc_table_1}.

Figure \ref{fig:wine_exp2_distr} shows the discretization result on variable $E$ and $K$. The discretization edge on variable $E$ is same as the edge found by the MDL principle and the proposed method in Figure \ref{wine_exp1_distr}. This indicates that some discretization edges are robust against the network structure.

\begin{figure}[ht]
    \begin{tabular}{cc}
    \centering
    \scalebox{0.7}{
      \input{graph_wine_2}}
    \end{tabular}
  \caption{The learned discrete-valued Bayesian network from the Wine dataset}
  \label{fig:wine_graph_2}
\end{figure}

\begin{figure}[ht]
    \begin{tabular}{cc}
      \input{graph_wine_exp2_distr_5_11}
    \end{tabular}
  \caption{Comparison of the raw data and discretization result on variable $E$ and $K$ according to Figure \ref{Auto_graph_2}}
  \label{fig:wine_exp2_distr}
\end{figure}
